---
title: "IntroductionToRASC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IntroductionToRASC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Install the package first:
```{r setup}
library(RASC)
```
Next we will convert the input data which is a dataframe that generated by single cell sequence into Single Cell Experiment by calling load_expression function:
```
expr <-load_expression(file_name)
```
Then we will load the gmt file which contains information about gene set that have the pathways you interested in:
eg:if you use hall_mark.gmt
```
load_AUCell_genesets(hall_mark.gmt)

```
Then we have all data set up, the next step is to rank the single cell experiment object with the pathway gene set by calling AUCell_Batch:
```
pathway_scores = AUCell_batch(counts(expr), genesets = c(hallmarks), num_batches=20)
```
Then we could visualize the result for given cells and pathways by calling PlotPathwayScores:
```
PlotPathwayScores(pathway_scores,1,10,pathway_names)
```
